\TitleFont Compressively sampled speech: How good is the recovery?

### 2020-10-19 Response to Reviewer Comments.tex

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\parindent=0pt
\parskip=10pt

\newcommand{\pagelineref}[1]{Page~\pageref{#1}, Line~\lineref{#1}}

@@

	\item
		\begin{enumerate}
			\item \textbf{Please incorporate changes that you mentioned in your reply to the reviewer but was not added to the manuscript. For example, add the conversion table from number to qualitative description -- "slightly below average".}

			We have added Table 1 in Sec.~2.4 for the conversion of PESQ from quantitative to qualitative. In the preceding paragraph, the following sentence has been added:

			\begin{quotation}
				...models the obsolete mean opinion scores (MOS). \textcolor{Green}{Its output is a float in the range $[1, 5]$ with corresponding qualitative descriptions at integer values, as shown in Table~1.}
			\end{quotation}
		\end{enumerate}
\end{enumerate}

\section*{List of Changes}

\begin{itemize}
	\item \textbf{Abstract}: Incorporated changes suggested by the reviewer.
	\begin{itemize}
		\item Last sentence: removed ``It is shown''
	\end{itemize}

	\item \textbf{Introduction}: Incorporated changes suggested by the reviewer.
	\begin{itemize}
		\item Paragraph 1: removed Eq.~(1) and replaced preceding sentence with ``...sampled at a rate at least twice the signal's highest frequency component.''
		\item Paragraph 2: replaced ``impossible'' with ``infeasible''
	\end{itemize}
	\item \textbf{Methodology}: Incorporated changes suggested by the reviewer.
	\begin{itemize}
		\item Sec.~2.2: replaced ``some domain'' with ``a domain''
		\item Sec.~2.4: added ``...which models the obsolete mean opinion scores (MOS) \textcolor{Green}{obtained from human observers}.''
	\end{itemize}
	\item \textbf{Results \& Discussion}: Incorporated changes suggested by the reviewer.
	\begin{itemize}
		\item Paragraph 1: replaced ``appears to have decreased'' with ``decreased''
		\item Last sentence: removed ``However''
	\end{itemize}
\end{itemize}

### 2020-10-19 main.tex
1st draft slides

\subsection{Reconstruction evaluation}\label{ssec:eval}
Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS). Its output is a float in the range $[1, 5]$ with corresponding qualitative descriptions at integer values, as shown in Table~\ref{tab:pesq}. Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual \cite{pesq} for an in-depth discussion.

@@

\begin{figure}[tbp]
	\centering
	\subfloat[Original]{\makebox[0.46\textwidth]{{\includegraphics[width=0.46\textwidth]{original.png}\label{fig:original}}}}
	\quad % or other spacing between figures
	\subfloat[Recovered]{\makebox[0.46\textwidth]{\includegraphics[width=0.46\textwidth]{recovered.png}\label{fig:recovered}}}
	\caption{Test speech signal obtained from the TIMIT speech corpus with the (a) original signal, and (b) reconstructed signal from compressive measurements. The top row is the representation in the time domain, while the bottom row is the spectrogram representation (25 ms sampling window with 75\% overlap). The signal reads ``She had your dark suit in greasy wash water all year''.}\label{fig:spectrogram}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=\textwidth]{metrics.png}
	\caption{Two most commonly used metrics in evaluating quality of reconstructed speech recordings. PESQ is sensitive to the signal compression (left), while the \snrseg~is sensitive to the number of subbands (right).}
	\label{fig:pesq-snr}
\end{figure}

>>>>

\subsection{Reconstruction evaluation}\label{ssec:eval}
Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS) obtained from human observers. Its output is a float in the range $[1, 5]$ with corresponding qualitative descriptions at integer values, as shown in Table~\ref{tab:pesq}. Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual \cite{pesq} for an in-depth discussion.

@@

\begin{figure}[tbp]
	\centering
	\subfloat[Original]{\makebox[0.46\textwidth]{{\includegraphics[width=0.45\textwidth]{original.png}\label{fig:original}}}}
	\quad % or other spacing between figures
	\subfloat[Recovered]{\makebox[0.46\textwidth]{\includegraphics[width=0.45\textwidth]{recovered.png}\label{fig:recovered}}}
	\caption{Test speech signal obtained from the TIMIT speech corpus with the (a) original signal, and (b) reconstructed signal from compressive measurements. The top row is the representation in the time domain, while the bottom row is the spectrogram representation (25 ms sampling window with 75\% overlap). The signal reads ``She had your dark suit in greasy wash water all year''.}\label{fig:spectrogram}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.89\textwidth]{metrics.png}
	\caption{Two most commonly used metrics in evaluating quality of reconstructed speech recordings. PESQ is sensitive to the signal compression (left), while the \snrseg~is sensitive to the number of subbands (right).}
	\label{fig:pesq-snr}
\end{figure}
